Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-01-17 Manuscript/manuscript.Rmd
editted intro

Commonly used measures of model performance for binary classifiers include the area under the receiver operating curve (AUROC). The popularity surrounding the use of ROC curves is that they do not depend on a threshold. However, when the prevalence of an event is low--that is, a defined genomic region containing a TAD boundary--mean probabilities are biased towards the majority class. This results in the area of interest under an ROC curve to be compressed toward a small corner in the ROC space [@prati2011survey]. While not directly affecting the value of the AUROC, this can have severe consequences on the interpretability of the model's performance. A better threshold-free measure to use when dealing with imbalanced data in the area under the precision-recall curve (AUPRC). It has been shown that the use of AUPRC with imbalanced datasets yields more accurate and intuitive interpretation of model performance when compared to AUROC [@saito2015precision]. Likewise, metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data. In each case, the weight

do not incorporate the entirety of the confusion matrix created when validating predictive models on a test data set. Therefore, each of these metrics are likely to be inflated when evaluating model performance. Better measures

[???include explanation of why included metrics are better]

>>>>

Commonly used measures of model performance for binary classifiers include the area under the receiver operating curve (AUROC). The popularity surrounding the use of ROC curves is that they do not depend on a threshold. However, when the prevalence of an event is low--that is, a defined genomic region containing a TAD boundary--mean probabilities are biased towards the majority class. This results in the area of interest under an ROC curve to be compressed toward a small corner in the ROC space [@prati2011survey]. While not directly affecting the value of the AUROC, this can have severe consequences on the interpretability of the model's performance. A better threshold-free measure to use when dealing with imbalanced data in the area under the precision-recall curve (AUPRC). It has been shown that the use of AUPRC with imbalanced datasets yields more accurate and intuitive interpretation of model performance when compared to AUROC [@saito2015precision]. Likewise, metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data. In each case, the weight of the measure is carried primarily by the correct classification of the majority class. Better measures to consider are the F1-Score and Matthew's Correlation Coefficient (MCC) [@jeni2013facing]. The F1-Score can be interpreted as a weighted average of the precision and recall values, while MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications. In either case, all 4 quadrants of the confusion matrix are used, making for more balanced measures in the case of imbalanced data [@chicco2017ten].

[???Now discuss sampling techniques to account for imbalanced data]
